---
title: "Data cleaning"
author: "Yufei Wu"
output: html_document
---

## Remark
Since the dataset for this project is too large to upload to GitHub, I reduced its size and saved the smaller version as an RDS file, treating it as the raw data. Here's the code I used to reduce size:

 # load packages
 library(here)
 library(dplyr)
 # load raw data
 LCAraw1 <- read.csv(here("data", "raw-data", "LCA2020to2024.csv"))
 # Shrink the data
 colnames(LCAraw1)
 LCAraw <- LCAraw1 %>%
   select(CASE_STATUS, VISA_CLASS, RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, WAGE_UNIT_OF_PAY, PREVAILING_WAGE, PW_UNIT_OF_PAY)
 # Save as rds
 save_data_location <- here::here("data","raw-data","LCAraw.rds")
 saveRDS(LCAraw, file = save_data_location)

# Setup

```{r}
# Load packages
library(here)
library(dplyr)
library(tidyverse)
```


# Data loading

```{r}
# load raw data
LCAraw <- readRDS(here("data", "raw-data", "LCAraw.rds"))
```


# Check data

```{r}
# Get the overview of the data
dim(LCAraw)
colnames(LCAraw)
str(LCAraw)
head(LCAraw)
```


# Cleaning

```{r}
# Keep only the certified case and H-1B visa, and remove these two column
LCAdata <- LCAraw %>%
  filter(CASE_STATUS == "Certified", VISA_CLASS == "H-1B")%>%
  select(RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, WAGE_UNIT_OF_PAY, PREVAILING_WAGE, PW_UNIT_OF_PAY)

# Check missing values per column
colSums(is.na(LCAdata))

# Remove missing values
LCAdata <- LCAdata %>% drop_na()

# Check again
colSums(is.na(LCAdata)) # now it is good

# Standardize all character columns to a consistent case (except state name)
LCAdata <- LCAdata %>%
  mutate(
    SOC_TITLE = tolower(SOC_TITLE),
    EMPLOYER_NAME = tolower(EMPLOYER_NAME)
  )

# take a look at the processed data
dim(LCAdata)
head(LCAdata)
```



# Save data 

```{r}
save_data_location <- here::here("data","processed-data","LCAdata.rds")
saveRDS(LCAdata, file = save_data_location)
```




